A Switching Planner for Combined Task and Observation Planning

### 2011-02-09 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
few small changes

@@

\small
\[
\reward(\state, \assumptiveDT{i}) = \bigg\{ \begin{array}{ll}
\$(T_i) & \pp{if}~\;\;T_i \not\subseteq \state \\
\hat\$(T_i) & \pp{otherwise} \\
\end{array}
\]
\normalsize

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a 
relatively small positive (negative) numeric quantity\footnote{Small
relative to rewards from the original process model.} which captures
the utility the agent receives for correctly (incorrectly) rejecting
an assumption.
%%
In terms of action physics, a disconfirm action can only be executed
once, and otherwise is modelled as self-transformation.
%%
We only consider {\em relevant} assumptions when constructing the
abstract model.  If \switchAction\ is the action that switched the
system to a DT session, then an assumption $\assumptiveS{i}$ is {\em
relevant} if it is necessary for the outcome of \switchAction\ to be
determined.  Continuing our simplified example, if the trace is:

@@

In order to guarantee fast DT sessions, planning occurs for a small
abstract problem. In our setting, where the underlying decision
process has a deterministic action model, a significant cause of
problem largeness is due to the number of states that occur with
non-zero probability in the underlying belief-state. In posing a small
abstract process for a DT session, we construct an abstract
belief-state that is chiefly characterised by facts related to the
current trace. In that abstraction, instances of operator or sense
declarations whose specification mentions an excluded fact are not
available.
%%
In detail, we first construct an $(\pp{:init})$ declaration which only
contains relevant assumptions from the trace -- e.g.,
(Fig.\ref{fig:abstraction-b}) gives an example, where diamonds are
probabilistic terms, and circles are atomic and/or conjunctive.
%%
For each excluded atom, we compute the {\em entropy} of the active
assumptions, {\em conditional} on that atom. Intuitively, lower
entropy indicates an atom gives better information about
assumptions. Facts are iteratively added to the belief-state in
increasing order according to that measure until the belief space size
reaches a predefined limit (Fig.\ref{fig:abstraction-c}).

>>>>

\vspace{-1ex}

@@

\vspace{-1ex}
\small
\[
\reward(\state, \assumptiveDT{i}) = \bigg\{ \begin{array}{ll}
\$(T_i) & \pp{if}~\;\;T_i \not\subseteq \state \\
\hat\$(T_i) & \pp{otherwise} \\
\end{array}
\]
\normalsize

\vspace{-1ex}

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a
small positive (negative) numeric quantity which captures
the utility the agent receives for correctly (incorrectly) rejecting
an assumption.
%%
In terms of action physics, a disconfirm action can only be executed
once, and otherwise is modelled as self-transformation.
%%
We only consider {\em relevant} assumptions when constructing the
abstract model.  If \switchAction\ is the action that switched the
system to a DT session, then an assumption $\assumptiveS{i}$ is {\em
relevant} if it is necessary for the outcome of \switchAction\ to be
determined.  Continuing our simplified example, if the trace is:

@@

In order to guarantee fast DT sessions, planning occurs for a small
abstract problem. In our setting, where the underlying decision
process has a deterministic action model, a significant cause of
problem largeness is due to the number of states that occur with
non-zero probability in the underlying belief-state. In posing a small
abstract process for a DT session, we construct an abstract
belief-state that is chiefly characterised by facts related to the
current trace. In that abstraction, instances of operator or sense
declarations whose specification mentions an excluded fact are not
available.
%%
In detail, we first construct an $(\pp{:init})$ declaration which
contains the root term, and relevant assumptions from the trace --
e.g., (Fig.\ref{fig:abstraction-b}) gives an example fragment, where
diamonds are probabilistic terms, and circles are atomic and/or
conjunctive.
%%
For each excluded atom, we compute the {\em entropy} of the active
assumptions, {\em conditional} on that atom. Intuitively, lower
entropy indicates an atom gives better information about
assumptions. Facts are iteratively added to the belief-state in
increasing order according to that measure until the belief space size
reaches a predefined limit (Fig.\ref{fig:abstraction-c}).
